### 2022-02-18 pre/pre.tex
unif

\subsection{Unification}
\subsection{Inference Rules}
\subsection{The Redundancy Criterion and Simplification Rules}
\subsection{The Saturation Procedure}

>>>>

\subsection{Unification}

Calculi from the resolution family, including superposition, perform inferences
only on unifiable terms. We say terms $s$ and $t$ are unifiable if there is a
substitution $\sigma$ such that $\sigmaterm{s} = \sigmaterm{t}$; we further say
$\sigma$ is the unifier. A \emph{unification constraint} $s \unif t$ is an unordered pair of two terms of
the same type. The most general unifier is a unifier $\sigma$, such that for any
other unifier $\theta$, there is a substitution $\varrho$ such that $\sigma =
\varrho\theta$. When there is such $\varrho$, we say $\sigma$ is more general
than $\theta$ In first-order logic, the most general unifier is unique up to
variable renaming. Furthermore, first-order logic admits efficient algorithms
for computing the most general unifier \cite{hv-09-unifalgs}.

In higher-order logic, unification is performed modulo rules of
$\alpha\beta\eta$ conversion. Under these conditions, the uniqueness of the most
general unifier is not guaranteed. Consider the unification of terms $X \,
(\cst{f} \, \cst{a})$ and $\cst{f} \, (X \, \cst{a})$. Any substitution of the
form $X \mapsto \lamx{\cst{f}^i \, x}$ is a unifier, with $\cst{f}^i \, x$
denoting iterated, $i$-fold application of $\cst{f}$. To generalize most general unifiers
to higher-order logic, the concept of complete sets of unifiers was introduced.

A (higher-order) \emph{unifier} of a multiset of unification constraints $E$ is
a substitution $\sigma$, such that $\sigma s \equi \sigma t$, for all $s \unif t
\in E$. A \emph{complete set of unifiers} (\emph{CSU}) of $E$ is defined as a
set $U$ of $E$'s unifiers along with a set $V$ of \emph{auxiliary variables}
such that no $s \unif t \in E$ contains variables from $V$ and for every unifier
$\rho$ of $E$, there exists a $\sigma \in U$ and a substitution $\theta$ such
that for all $X\not\in V,$ $\rho X = \theta\sigma X$. The most general
unifier corresponds is a one-element CSU. A unifier of terms $s$ and $t$ is a
unifier of the singleton multiset $\{ s \unif t \}$.

\subsection{Inference Rules}
\subsection{The Redundancy Criterion and Simplification Rules}
\subsection{The Saturation Procedure}
